Measuring and optimizing machine learning interpretability

### 2019-05-22 2019-05-sommerklausur/2019-sommerklausur-molnar.Rmd
adds slides for sommerklausur

---
title: "Measuring and optimizing machine learning interpretability"
author: "Christoph Molnar, Giuseppe Casalicchio, Bernd Bischl"
date: "DagStat 2019-03-21"
institute: "LMU Munich"
output: 
  beamer_presentation:
    includes:
      in_header: "header_pagenrs.tex"
---

@@

## Interested in interpretable machine learning?
More on interpretable machine learning in my book [http://christophm.github.io/interpretable-ml-book/](http://christophm.github.io/interpretable-ml-book/).

```{r, out.width="5cm"}
knitr::include_graphics("../images/cover-bordered.jpg")
```

>>>>

---
title: "Measuring and optimizing machine learning interpretability"
author: "Christoph Molnar, Giuseppe Casalicchio, Bernd Bischl"
date: "Sommerklausur 2019-05-24"
institute: "LMU Munich"
output: 
  beamer_presentation:
    includes:
      in_header: "header_pagenrs.tex"
---

@@

# The End

## Why not GAM?

```{r echo = TRUE}
library("mgcv")
library("iml")
set.seed(42)
X = data.frame(x1 = rnorm(100), x2 = rnorm(100))
f = function(model = NULL, newdata) {
	1 *  (newdata[,1] > 0)
}
y = f(newdata = X)
dat = cbind(y, X)
mod.gam = gam(y ~ s(x1) + s(x2), data = dat)

```

## Why not GAM?

```{r fig.height = 5}
plot(mod.gam)
```

## Why not GAM?

```{r}
pred = Predictor$new(predict.fun = f, data = X)
fes = FeatureEffects$new(pred)
plot(fes, ncol = 2)
```
